DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
microtype
line breaks

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{epstopdf} %converting to PDF
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

@@

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. the stability and safety specifications by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

Instead of unfolding the dynamics, the second approach (shown in Fig.~\ref{fig:CEGARIS}) 
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to 
simultaneously evaluate all possible progressions of the model. This eliminates the need for
a completeness threshold, since the time horizon considered in abstract acceleration is infinite.
An additional preprocessing phase is used to compute 
a set of initial bounds on $K$ based on input constraints. 
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
%
Since this model is based on abstraction, we initially perform the synthesis over a basic
model that abstracts away the complexity of the specification and is only refined to a more
complex model when a counterexample is found. 
% Thus, we may only look at the gain of the
% model to synthesise a controller and to add further restrictions on specific sections of the reach
% tube when these prove to invalidate the solution.
The use of this Counterexample-Guided 
Abstraction-Refinement results in much faster synthesis and verification since it is applied to
both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.

@@

Regarding the state-space representation, we have reproduced the stability property for 
the closed-loop control system of a pendulum represented by Eq.~\eqref{ss-synth-controller}. 
%
\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}

Where,
%
$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$

>>>>

\usepackage{microtype}
\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{epstopdf} %converting to PDF
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

@@

\begin{abstract}
%
We present an automated MATLAB Toolbox, named as DSSynth (Digital-System
Synthesizer), to synthesize sound digital controllers for physical plants
that are represented as linear time-invariant systems with single input and
output.  In particular, DSSynth synthesizes digital controllers that are
sound w.r.t.  the stability and safety specifications by taking into account
finite word-length effects in their representation.  DSSynth considers the
complete range of approximations, including time discretization,
quantization effects, and finite-precision arithmetic (and its rounding
errors).  Currently, there are two DSSynth versions for synthesizing digital
controllers for physical plants represented by transfer function or
state-space equations: a command-line and a MATLAB application.  The
resulting toolbox enables application of program synthesis to real-world
control engineering systems.
%
\end{abstract}

@@

Instead of unfolding the dynamics, the second approach (shown in
Fig.~\ref{fig:CEGARIS}) employs {\em abstract
acceleration}~\cite{cattaruzza2015unbounded} to simultaneously evaluate all
possible progressions of the model.  This eliminates the need for a
completeness threshold, since the time horizon considered in abstract
acceleration is infinite.  An additional preprocessing phase is used to
compute a set of initial bounds on $K$ based on input constraints.  Note
that these bounds will be used by the {\sc synthesize} phase to reduce the
size of the solution space.
%
Since this model is based on abstraction, we initially perform the synthesis
over a basic model that abstracts away the complexity of the specification
and is only refined to a more complex model when a counterexample is found.
%
% Thus, we may only look at the gain of the
% model to synthesise a controller and to add further restrictions on specific sections of the reach
% tube when these prove to invalidate the solution.
%
The use of this Counterexample-Guided Abstraction-Refinement results in much
faster synthesis and verification since it is applied to both phases,
allowing for faster results whilst maintaining soundness for an infinite
time horizon.

@@

Regarding the state-space representation, we have reproduced the stability property for 
the closed-loop control system of a pendulum represented by Eq.~\eqref{ss-synth-controller}. 
%
\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}
%
\noindent where,
%
$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$
